Searching for long-period transiting planets in the \kepler\ light curves using supervised classification

### 2015-04-08 document/ms.tex
candidates figure

>>>>

As a demonstration of the feasibility of this method to search for single
transit events, we selected 3500 bright, Sun-like stars based on the revised
stellar parameters collected and measured for a recent \kepler\ data release
\citep{Huber:2014}.
The targets were selected in the parameter range
\begin{itemize}

\item effective temperature:
        $4100\,\mathrm{K} < T_\mathrm{eff} < 6100\,\mathrm{K}$,

\item surface gravity:  $4.0 < \log g < 4.9$, and

\item \kepler\ magnitude: $15 > K_\mathrm{p} > 10$.

\end{itemize}

This search results in 596 candidate transits in the light curves of these
3500 stars.
The vast majority of these candidates are misclassified false positives and
many of them are caused by astrophysical sources.
To weed out known astrophysical sources, we cross-match this list against
known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
variability \citep{McQuillan:2014}.
Removing these signals results in 273 candidates.
